THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-06-30 DishReflectometry/Paper1_v2.tex
Second edit with figure 7, 8 replacing fig 4,5

Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise and foregrounds four to five orders of magnitude
brighter than the signal ~\citep{2015ApJ...801..138P}, 
sky-averaged 21~cm monopole experiments such as
EDGES; ~\citep{baars_et_al1977},
BIGHORNS; ~\citealt{XXX},
SARAS; ~\citep{Patra_et_al1999} ,
SCIHI; ~\citealt{2015PhDT........65V},
HYPERION; ~\citep{presley_et_al2015}
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

\noindent
%Defining $a=\volt_{rec}/\volt_{sky}$ and we see that 
Hence,
 \begin{eqnarray}
{\volt_{rec}\over \volt_{sky} } & = &   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}\nonumber\\
& = & \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} 
 \label{eq:Sigma}
\end{eqnarray}
Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).  We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.  Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).

@@

An accurate measurement of this quantity requires receiving $v_{sky}$ from a well calibrated, wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission. While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq:Sigma} could be measured using the return loss measurement technique with a vector network analyzer (VNA). \\
\indent A VNA is connected to the HERA element via a 50-foot cable. It then transmits a broadband noise voltage, $\volt_{trans}$, and a factor $(1+\Gamma_f)$ of this voltage is radiated by the feed while the fraction $\Gamma_{f}$ returns to the VNA. Although the radiated signal illuminates the dish and most of it is radiated into free space, a fraction $\Gamma_d$ of this signal is reflected back towards the feed, and $(1+\Gamma_f)$ is received by the VNA.  The received voltage, after $n$ reflections between the dish and the feed (where again $n=0$ is the first reflected signal at the reference plane), is therefore:

\begin{eqnarray}
\volt_{rec} & = &  \Gamma_f \volt_{trans} \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \Gamma_d\Gamma_f\dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n \nonumber \\
\end{eqnarray}
Therefore, 
\begin{equation}
{\volt_{rec}\over \volt_{trans} } = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\label{eq:s11}
\end{equation}
The VNA measures the quantity $\volt_{rec}/\volt_{trans}=s_{11}$ which is the voltage reflection coefficient of the HERA element.
The fundamental differences between the right hand side of equations \ref{eq:Sigma} and \ref{eq:s11} are the $n=0$ term and the multiplicative factor in front of the convergent series $\displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}$ that represents the contribution of the delayed voltage components at the VNA input, arising due to multiple signal reflections between the feed and the dish. Finally, writing $\volt_{rec}/\volt_{trans}=s_{11}$, equation \ref{eq:s11} can be written as,
\begin{equation}
s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\end{equation}
Comparing to Eq. \ref{eq:Sigma} and we find that
\begin{eqnarray}
{\volt_{rec}\over \volt_{sky} } & = & (1+\Gamma_d)\left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right] \nonumber\\
 & = & \bmvolt(\thhat,\nu) \left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
\end{eqnarray}
When the feed return loss is measured separately, all the higher order terms of equation \ref{eq:s11} do not exist. In this case, $\Gamma_f = s_{11}^{f}$. Using this measurement and the VNA measurement of $s11$, the quantity $v_{rec}\over v_{sky}$ is estimated. \\
%
\indent From this, for a two element interferometer with identical antenna elements, the ratio of the received sky intensity to true sky intensity will be, 
\begin{eqnarray}
{I_{rec}\over I_{sky} } & = & \Bigg|{\volt_{rec}\over \volt_{sky} }\Bigg|^2 =  \beam(\thhat,\nu)\times \nonumber\\
             && \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right)\right] + \nonumber\\ 
             &&  \left[ \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2  \right]  \nonumber\\
\label{eq:power_ratio}             
\end{eqnarray}

@@

Comparing equations \ref{eq:power_ratio} and \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of equation \ref{eq:power_ratio}. In the ideal case, $\Gamma_{f}=0$, in which case equation \ref{eq:power_ratio} results in equation \ref{eq2}. The Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
In the delay domain, visibilities contributed to by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$. These will broaden the width of the delay spectrum, which ultimately interferes with the 21cm power spectrum detection.
% Combining these terms, the expression of visibility will be,

%\begin{eqnarray}\label{eqn:series1}
%\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
%			& = & \int I_{sky}(\vec b, \nu)A(\thhat,\nu) \ifngexp d\Omega
%\end{eqnarray}
%%%where we define a combined common instrument parameter, written as, 
%%% \begin{eqnarray}
%%%\Sigma(\thhat, \nu) & = & \beam_{f}  [ 1+  \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
%%%&& + (\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
%%%&&  ....+(\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n}  ]\\
%%%& = & \beam_{f}+\beam_{f} \displaystyle\sum\limits_{n=1}^{n} [2\Re( \Gamma_{f}\Gamma_{d}\dfngexp)]^{n}
%%%   \nonumber\\ 
%%%   \label{eq6}
%%%\end{eqnarray}
%%%where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}= |a(1-\Gamma_{f})|^{2}$ is the antenna cross power pattern.
%and the delay spectrum would be, 
%\begin{eqnarray}
%\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
%\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\vec b, \nu) \ast A(\vec b, \nu) \right]\dfngexp d\Omega
%\label{eq7}
%\end{eqnarray}

% Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. \\

%In a related series of papers, Thyagarajan et al. (2016) have shown the simulated sensitivity calculations of HERA for various antenna element responses (Figure \ref{fig:sim_limit_delay}) using a comprehensive foreground model as well as a model for the EoR power spectrum. From these simulations, Figure \ref{fig:sim_limit_delay} (Thyagarajan et al.) shows the level of attenuation required for the multiply reflected sky signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements. Ewall-Wice et al. (2016) has simulated the time domain response of the HERA element considering multiple reflections between the feed and the dish.  Figure \ref{fig:sim_limit_delay} shows the simulated cross-power response of a pair of HERA antennas as a function of time (Ewall-wice et al.). These simulations set up the performance criterion for the HERA antenna element.
% \begin{figure*}[ht]
%\begin{minipage}[b]{0.5\linewidth}
%\centering
%\includegraphics[angle=0, width=\linewidth]{plots/sim_limit.jpg}
%\end{minipage}
%\hspace{0.1cm}
%\begin{minipage}[b]{0.5\linewidth}
%\centering
%\includegraphics[angle=0, width=\linewidth]{plots/sim_delay.jpg}
%\end{minipage}
%\caption{Left: Signal attenuation required for the reflected sky power arriving at the feed at higher delays, as estimated from the simulated antenna beam and foreground models (Thyagarajan et al.). The three different contours show three different system performance requirements based on the simulated response of the HERA element for a measurement frequency of 150MHz, corresponding to the redshift of $z=8.47$, and a 14.5m baseline. The instrumental requirements become extremely stringent for the detection of the smaller $k_\parallel$ values, corresponding to very large spatial scales. Right: The simulated cross power response kernel for HERA. The simulation assumes an achromatic beam with the chromaticity attributed entirely to the multiple reflections between the dish and the feed. This shows the level to which the multiple reflections at the higher delays is expected to be reduced following the dish and feed designs.} %Some explanation of the left hand axis of the right panel figure would be really nice in here since this is the only mention of R(tau), and it's new notation compared to the rest of the paper.
%\label{fig:sim_limit_delay}       
%\end{figure*}

%signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
%at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
%signal at the feed ~\citep{parsons_deboer_memo}. This specification was
%approximated based on the power level of the cosmological signal in relation to
%foreground signals, which is estimated to be six orders of magnitude fainter
%~\citep{santos_et_al2005,  ali_et_al2008,deoliveira2008, jelic_et_al2008, bernardi_et_al2009,bernardi_et_al2010, ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
%Additionally, the $14m$ HERA baselines set a foreground containing
%horizon-limit (the wedge) that, with some buffer, sets a delay specification of
%$60ns$
%~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements. 
%++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{\textbf{Reflectometry measurements}}
\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{The HERA feed consists of a pair of crossed-dipoles ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the crossed-dipoles in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}

Reflectometry measurements are carried out at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016 (in prep). \\
A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish. This measurement is 
Section 3 laid the mathematical framework of how the delay spectrum is estimated from the return loss measurement. The return loss of the feed while  facing up the sky as well as while suspended on the dish and ${I_{rec}\over I_{sky}}$  is shown in figure \ref{fig:all_RL}.

Reflectometry measurements were carried out on the prototype HERA element in Green
Bank, WV, (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance. The HERA element consists of a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair -- identical to the feed of the PAPER antenna -- as a feed, which is suspended at the focal plane of the dish, where the focal height is $5m$, with the support of three vertical poles. The HERA elements are closely spaced, with the centre-to-centre distance between two dishes equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed-dipole feed and the back plane are encased in a cylindrical cage. The feed is raised and lowered by a three-pulley system mounted on the three poles. The detailed geometry and electromagnetic design of the feed is presented in deBoer et al. 2016 (in prep). \\
\indent A VNA is connected via a 50-ft cable at the feed output of the HERA element, and the return loss $(s_{11})$ is measured as a function of frequency while the feed is suspended at the focal plane of the dish. Section 3 laid the mathematical framework for how the delay spectrum is estimated from the return loss measurement.

%, if the incident power from the sky signal is $I_{sky}$, the feed
%reflection coefficient is $\Gamma_{f}$, and the dish reflection
%coefficient is $\Gamma_{d}$, then the net power entering a feed after
%$n^{th}$ reflection off the feed and the dish is:

%\begin{eqnarray}
%\tilde I_{meas}(\vec b, \nu) & = & \int I_{sky}(\vec b, \nu)A(\vec b, \nu) \dfngexp d\Omega
%\end{eqnarray}

@@

%
Return loss measurements are similar to auto correlation measurements from a single HERA element. Given our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power, or the visibility $\vis (\vec b, \nu)$, between the two antennas with a normalization factor of $2$. 
%
\section{Results}
\begin{figure}[ht]
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/RL_mag.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/RL_phse.png}
\end{minipage}
\caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser. Right panel shows the corresponding phase. Return loss of the feed alone is shown in green while the same for the feed+dish assembly is shown in blue. Finally, the quantity of interest ${I_{rec}\over I_{sky}}$ is shown in red. In ideal condition 100\% of the sky power is to be received and ${I_{rec}\over I_{sky}} = 1$ or 0dB. Finite return loss at the antenna input deviate this quantity from its ideal value and ${I_{rec}\over I_{sky}} < 1$. Also, frequency dependence of the feed and the dish as well as the multiple reflections introduces the small scale fluctuations as seen in the red curve. }
% HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift. The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance. }
\label{fig:all_RL}
\end{figure}
\begin{figure}       
\centering
\includegraphics[width=\linewidth]{plots/H_dish_feed.png}
\caption{Delay spectrum of the HERA element (blue) the HERA feed (green) estimated by taking the Fourier transform of the measured return loss of power at the feed output. The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure. After correcting the measurements from the transmission mode to reception mode by equation \ref{eq:power_ratio} the delay spectrum in the receiving mode is estimated (red). }
\label{fig:delay_spectrum}
\end{figure}

Figure \ref{fig:all_RL} shows the return loss measured between $100$ to
$200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}. Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution. A number of systematic effects as well as mathematical artefacts that are critical to this measurements and corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.

\subsection{\textbf{Feed effect:zero delay correction}}
%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.

While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatch in between the feed and the 50 Ohm transmission line. In delay domain, this appears at the zero delay bin. The zero delay response is identical whether or not the feed is suspended on the dish and  Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky. This results in feed return loss alone including the surrounding cage structure but excluding the dish response. While $\Gamma_{f}$ fraction of power is reflected off the feed, $1+\Gamma_{f}$ fraction of the power gets transmitted. In receiving mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected back in to the space while $1+\Gamma_{f}$ voltage enters the feed. In receiving mode, in delay domain, this appears at the zero delay bin.
The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated. Magnitude and phase of $\Gamma_{f}$ , $s_{11}$ and ${I_{rec}\over I_{sky}}$ is shown in figure \ref{fig:all_RL}.

Figure \ref{fig:freq} shows the return loss measured between $100$ to
$200$ MHz when the feed is suspended at the focal plane of the parabolic dish -- $5m$ from the dish vertex. This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}. The measurement bandwidth is kept much larger than the bandwidth of operation to achieve a higher delay resolution. A number of systematic effects, as well as mathematical artifacts critical to these measurements and the corresponding estimation of the delay spectrum, are taken in to account in determining the delay spectrum and are described below.

>>>>

Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise and foregrounds four to five orders of magnitude
brighter than the signal ~\citep{2015ApJ...801..138P}, 
sky-averaged 21~cm monopole experiments such as
EDGES; ~\citep{Bowman_et_al2010},
BIGHORNS; ~\citealt{XXX},
SARAS; ~\citep{Patra_et_al2015} ,
SCIHI; ~\citep{2015PhDT........65V},
HYPERION; ~\citep{presley_et_al2015}
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

\noindent
%Defining $a=\volt_{rec}/\volt_{sky}$ and we see that 
Hence,
 \begin{eqnarray}
{\volt_{rec}\over \volt_{sky} } & = &   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}\nonumber\\
& = & \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} 
\label{corrected_response}
\end{eqnarray}
Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).  We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.  Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).

@@

An accurate measurement of this quantity requires receiving $v_{sky}$ from a well calibrated, wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission. While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq:Sigma} could be measured using the return loss measurement technique with a vector network analyzer (VNA). \\
\section{\textbf{Reflectometry measurements}}

Reflectometry measurements are carried out at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016. \\
%A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish.

 A VNA is connected to the HERA element via a 50-foot cable. It then transmits a broadband noise voltage, $\volt_{trans}$, and a factor $(1+\Gamma_f)$ of this voltage is radiated by the feed while the fraction $\Gamma_{f}$ returns to the VNA. Although the radiated signal illuminates the dish and most of it is radiated into free space, a fraction $\Gamma_d$ of this signal is reflected back towards the feed, and $(1+\Gamma_f)$ is received by the VNA.  The received voltage, after $n$ reflections between the dish and the feed (where again $n=0$ is the first reflected signal at the reference plane), is therefore:

\begin{eqnarray}
\volt_{rec} & = &  \Gamma_f \volt_{trans} \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \Gamma_d\Gamma_f\dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n \nonumber \\
\end{eqnarray}
Therefore, 
\begin{equation}
{\volt_{rec}\over \volt_{trans} } = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\label{eq:s11}
\end{equation}
The VNA measures the quantity $\volt_{rec}/\volt_{trans}=s_{11}$ which is the voltage reflection coefficient of the HERA element.
The fundamental differences between the right hand side of equations \ref{eq:Sigma} and \ref{eq:s11} are the $n=0$ term and the multiplicative factor in front of the convergent series $\displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}$ that represents the contribution of the delayed voltage components at the VNA input, arising due to multiple signal reflections between the feed and the dish. Finally, writing $\volt_{rec}/\volt_{trans}=s_{11}$, equation \ref{eq:s11} can be written as,
\begin{equation}
s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\end{equation}
Comparing to Eq. \ref{eq:Sigma} and we find that
\begin{eqnarray}
{\volt_{rec}\over \volt_{sky} } & = & (1+\Gamma_d)\left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right] \nonumber\\
 & = & \bmvolt(\thhat,\nu) \left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
\label{zero_delay_correction}
\end{eqnarray}
When the feed return loss is measured separately, all the higher order terms of equation \ref{eq:s11} do not exist. In this case, $\Gamma_f = s_{11}^{f}$. Using this measurement and the VNA measurement of $s11$, the quantity $v_{rec}\over v_{sky}$ is estimated. \\
%
\indent From this, for a two element interferometer with identical antenna elements, the ratio of the received sky intensity to true sky intensity will be, 
\begin{eqnarray}
{I_{rec}\over I_{sky} } & = & \Bigg|{\volt_{rec}\over \volt_{sky} }\Bigg|^2 =  \beam(\thhat,\nu)\times \nonumber\\
             && \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right)\right] + \nonumber\\ 
             &&  \left[ \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2  \right]  \nonumber\\
\label{eq:power_ratio}             
\end{eqnarray}

@@

Comparing equations \ref{eq:power_ratio} and \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of equation \ref{eq:power_ratio}. In the ideal case, $\Gamma_{f}=0$, in which case equation \ref{eq:power_ratio} results in equation \ref{eq2}. The Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
In the delay domain, visibilities contributed to by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$. These will broaden the width of the delay spectrum, which ultimately interferes with the 21cm power spectrum detection.

\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{The HERA feed consists of a pair of crossed-dipoles ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the crossed-dipoles in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}

@@

The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{meas_sim_RL_feed} and figure \ref{meas_sim_RL_HERA}.
\begin{figure}[ht]
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_mag.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_ph.png}
\end{minipage}
\caption{Magnitude and phase of the return loss of the feed as simulated and measured. While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements. The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input. }   
\label{meas_sim_RL_feed}
\end{figure}

\section{Results}
\begin{figure}       
\centering
\includegraphics[width=\linewidth]{plots/H_dish_feed.png}
\caption{Delay spectrum of the HERA element (green) the HERA feed (blue) estimated by taking the Fourier transform of the measured return loss of power at the feed output. The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure. After correcting the measurements from the transmission mode to reception mode by equation \ref{eq:power_ratio} the delay spectrum in the receiving mode is estimated (red). }
\label{fig:delay_spectrum}
\end{figure}

Figure \ref{meas_sim_RL_HERA} shows the return loss measured between $100$ to
$200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. This measurement is first correc ted to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}. The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}. Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution. A number of systematic effects as well as mathematical artefacts that are critical to this measurements and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.

\subsection{\textbf{Zero delay correction}}
%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.

While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatch in between the feed and the 50 Ohm transmission line. In delay domain, this appears at the zero delay bin. The zero delay response is identical whether or not the feed is suspended on the dish. Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky. This results in feed return loss alone including the surrounding cage structure but excluding the dish response. While $\Gamma_{f}$ fraction of incident voltage is reflected off the feed, $1+\Gamma_{f}$ fraction of the voltage is transmitted. In receiving mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected back in to the space while $1+\Gamma_{f}$ voltage enters the feed. In receiving mode, in delay domain, this appears at the zero delay bin.
The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.

\subsection{\textbf{Antenna beam pattern and feed return loss}}
The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna. Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$. Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.  The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line. While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum. However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant. During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna (need reference) which provides greater than 10dB return loss of power at the feed output.These baluns are under further design improvements aiming at 10 to 20dB better imepedance match between the feed and the balun than the measurements presented here.  Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{meas_sim_RL_feed}. This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.
